Increasing the topological gap by an order of magnitude through the geometry for Majorana SNS junctions.

### 2019-02-07 paper/snakemajoranas.tex
fix typo
add lenght of system in the wf plot

\comment{Majoranas are mostly made in hybrid NS structures.}
The current experimental effort ~\cite{mourik_signatures_2012,das_zero-bias_2012,deng_anomalous_2012,churchill_superconductor-nanowire_2013,zhang2018quantized} focuses on creating pairs of MBSs in hybrid normal-superconductor (NS) structures, where a long strip (or wire) of a semiconductor is interfaced with a superconductor.~\cite{lutchyn_majorana_2010,oreg_helical_2010}
Within the right parameter regime ($E_z^2>\mu^2+\Delta^2$ for a simple wire), the semiconductor becomes topological while MBSs appear at the ends of the segment.
Recently, a system with a slight modification has been proposed\cite{pientka2017topological}, where instead of having one superconductor, there are two superconductors, creating a superconductors-normal-superconductor (SNS) junction.
The additional superconductor adds an extra knob to adjust, the superconducting phase difference $\phi$, and this should make it easier to tune the system into the topological phase.
Recently, two groups~\cite{fornieri_evidence_2018,ren_topological_2018} have realized this system experimentally.
In practice, multiple problems arise making even the observation difficult, rendering the manipulation of Majoranas in the near future, unprobable.

@@

\begin{figure}[!htb]
\includegraphics[width=0.95\columnwidth]{figures/bandstructures}
\caption{Figure of the bandstuctures corresponding to the system in Fig.~\ref{fig:setup}.
Blue lines correspond to $\phi=0$, $B=0$ and red lines to $\phi=\pi$, $B = \SI{1}{T}$.
The three subplots are for different amplitudes of the zigzag, with (a) $z_y=0$, (b) $z_y=\frac{W}{4}$, and (c) $z_y=\frac{W}{2}$, where $W=\SI{200}{\nm}$ is the junction width.
We observe that once there are no more straight trajectories inside the junction (when $z_y=\frac{W}{2}$) the spectrum becomes most insensitive to the momentum $k_x$.
The parameters values are written on the bottom of Sec.~\ref{sec:physical_picture}.\label{fig:bandstuctures}}
\end{figure}

@@

\begin{figure}[!htb]
\includegraphics[width=0.95\columnwidth]{figures/wavefunctions}
\caption{Density of wavefunctions $\left|\psi\right|^2$ for sizes and geometries.
With (a) a straight system, (b) a saw-toothed zigzag system, (c) a system where the normal region is defined by lines parallel to a sinusoid, and (d) similar to (c) but with disordered edges.
Inside the figure, we indicate the Majorana length (or coherence length) $\lambda_\textrm{M}$ and the topological energy gap $E_\textrm{gap}$.
We observe that $\xi$ for (a) is significantly longer and $E_\textrm{gap} = E_\textrm{1} - E_M$ orders of magnitude smaller than for (b), (c), and (d), meaning that the details of the geometry do not matter for the improvements to occur.
The parameters values are written on the bottom of Sec.~\ref{sec:physical_picture}.\label{fig:wavefunctions}}
\end{figure}

@@

\begin{figure}[!htb]
\includegraphics[width=0.95\columnwidth]{figures/phasediagrams}
\caption{Phase diagrams of a straight system (a), (b) and zigzag system (c), (d), where (a), (c) are $E(\mu, B)$ and (b), (d) are $E(\phi, B)$.
Phase diagrams of a straight system (a), (b) and zigzag system (c), (d), where (a), (c) are $E(\mu, B)$ and (b), (d) are $E(\phi, B)$.
We compute the dispersion of the translationally invariant realizations of a straight and saw-toothed zigzag system and find $\min{E(k)}$ to obtain the energy gap.
% Additionally, use a generalized eigenvalue problem to find all phase boundaries at once.
The parameters values are written on the bottom of Sec.~\ref{sec:physical_picture}, except with $a=\SI{5}{\nm}$ and $L_\textrm{SC}=\SI{800}{\nm}$.
The chemical potential is $\mu=\SI{10}{\meV}$ in (b) and (d) and the superconducting phase is $\phi=\pi$ in (a) and (c).
\label{fig:phasediagrams}}
\end{figure}

>>>>

\comment{Majoranas are mostly made in hybrid NS structures.}
The current experimental effort ~\cite{mourik_signatures_2012,das_zero-bias_2012,deng_anomalous_2012,churchill_superconductor-nanowire_2013,zhang2018quantized} focuses on creating pairs of MBSs in hybrid normal-superconductor (NS) structures, where a long strip (or wire) of a semiconductor is interfaced with a superconductor.~\cite{lutchyn_majorana_2010,oreg_helical_2010}
Within the right parameter regime ($E_z^2>\mu^2+\Delta^2$ for a simple wire), the semiconductor becomes topological while MBSs appear at the ends of the segment.
Recently, a system with a slight modification has been proposed\cite{pientka2017topological}, where instead of having one superconductor, there are two superconductors, creating a superconductors-normal-superconductor (SNS) junction.
The additional superconductor adds an extra knob to adjust, the superconducting phase difference $\phi$, and this should make it easier to tune the system into the topological phase.
Recently, two groups~\cite{fornieri_evidence_2018,ren_topological_2018} have realized this system experimentally.
In practice, multiple problems arise making even the observation difficult, rendering the manipulation of Majoranas in the near future, improbable.

@@

\begin{figure}[!htb]
\includegraphics[width=0.95\columnwidth]{figures/bandstructures}
\caption{Figure of the bandstuctures corresponding to the system in Fig.~\ref{fig:setup}.
Blue lines correspond to $\phi=0$, $B=0$ and red lines to $\phi=\pi$, $B = \SI{1}{T}$.
The three subplots are for different amplitudes of the zigzag, with (a) $z_y=0$, (b) $z_y=\frac{W}{4}$, and (c) $z_y=\frac{W}{2}$, where $W=\SI{200}{\nm}$ is the junction width.
We observe that once there are no more straight trajectories inside the junction (when $z_y=\frac{W}{2}$) the spectrum becomes most insensitive to the momentum $k_x$.
The parameters values are written at the bottom of Sec.~\ref{sec:physical_picture}.\label{fig:bandstuctures}}
\end{figure}

@@

\begin{figure}[!htb]
\includegraphics[width=0.95\columnwidth]{figures/wavefunctions}
\caption{Density of wavefunctions $\left|\psi\right|^2$ for sizes and geometries.
With (a) a straight system, (b) a saw-toothed zigzag system, (c) a system where the normal region is defined by lines parallel to a sinusoid, and (d) similar to (c) but with disordered edges.
Inside the figure, we indicate the Majorana length (or coherence length) $\lambda_\textrm{M}$ and the topological energy gap $E_\textrm{gap}$.
We observe that $\xi$ for (a) is significantly longer and $E_\textrm{gap} = E_\textrm{1} - E_M$ orders of magnitude smaller than for (b), (c), and (d), meaning that the details of the geometry do not matter for the improvements to occur.
The length of the system is $3L_x=\SI{3900}{\nm}$, the remaining parameters values are written at the bottom of Sec.~\ref{sec:physical_picture}.\label{fig:wavefunctions}}
\end{figure}

@@

\begin{figure}[!htb]
\includegraphics[width=0.95\columnwidth]{figures/phasediagrams}
\caption{Phase diagrams of a straight system (a), (b) and zigzag system (c), (d), where (a), (c) are $E(\mu, B)$ and (b), (d) are $E(\phi, B)$.
Phase diagrams of a straight system (a), (b) and zigzag system (c), (d), where (a), (c) are $E(\mu, B)$ and (b), (d) are $E(\phi, B)$.
We compute the dispersion of the translationally invariant realizations of a straight and saw-toothed zigzag system and find $\min{E(k)}$ to obtain the energy gap.
% Additionally, use a generalized eigenvalue problem to find all phase boundaries at once.
The parameters values are written at the bottom of Sec.~\ref{sec:physical_picture}, except with $a=\SI{5}{\nm}$ and $L_\textrm{SC}=\SI{800}{\nm}$.
The chemical potential is $\mu=\SI{10}{\meV}$ in (b) and (d) and the superconducting phase is $\phi=\pi$ in (a) and (c).
\label{fig:phasediagrams}}
\end{figure}
